\hypertarget{age-of-sigmar-cheet-sheet}{%
\section{Age of Sigmar Cheet Sheet}\label{age-of-sigmar-cheet-sheet}}

\href{https://1d4chan.org/wiki/Age_of_Sigmar/Tactics/Order/Daughters_of_Khaine}{Tactics}
\#\# Checklist: \#\#\#\# Before you start: - Pick a temple with its
abilities (Benefits for army building in book) - Priests get additional
spells - Wizzards get additional spells

\hypertarget{gamephase}{%
\subsection{Gamephase}\label{gamephase}}

\hypertarget{heldenphase}{%
\paragraph{1. Heldenphase}\label{heldenphase}}

\begin{itemize}
\item
  \textbf{Baserule \textbar{} Spend Command Point} Helden: Im
  Laufschritt \textbar{} Vorwärts zum Sieg \textbar{} Ermutigende
  Gegenwart
\item
  \textbf{Morathi \textbar{} Worship Through Bloodshed}: If Morathi,
  High Oracle of Khaine is your general, you can use this ability. If
  you do, pick up to 2 friendly DAUGHTERS OF KHAINE units within 14" of
  Morathi (you cannot choose Morathi herself ). Those units can
  immediately shoot as if it were the shooting phase. Alternatively, if
  either unit is within 3" of an enemy unit, it can instead be chosen to
  pile in and attack as if it were the combat phase.
\item
  \textbf{Morathi \textbar{} Monstrous Transformation}: At the start of
  your hero phase, Morathi can transform into her monstrous aspect. See
  the Morathi, the Shadow Queen warscroll (pg 77) for a description of
  how Morathi transforms.
\item
  \textbf{Morathi \textbar{} The Truth Revealed}: If Morathi is wounded,
  there is a chance she will no longer be able to contain her wrath and
  will transform into her monstrous aspect. Roll a dice at the start of
  your hero phase. If the result is equal to or less than the number of
  wounds currently allocated to Morathi, she transforms as described on
  the Morathi, the Shadow Queen warscroll (pg 77).
\item
  \textbf{Morathi \textbar{} Enchanting Beauty}: Subtract 1 from the hit
  rolls of attacks that target Morathi, High Oracle of Khaine.
\item
  \textbf{Morathi the shadow queen} cast three spells, attempt to unbind
  two spells: She knows the Arcane Bolt, Mystic Shield and Arnzipal's
  Black Horror spells.
\item
  \textbf{Hag Queen \textbar{} Priestess of Khaine}: In your hero phase,
  a Hag Queen can pray once. If she does, pick a prayer she knows and
  roll a dice. On a result of 1 she is found unworthy and suffers 1
  mortal wound. On a 2 nothing happens. On a 3+ the prayer is successful
  and its effect takes place. A Hag Queen knows the Rune of Khaine and
  Touch of Death prayers
\item
  \textbf{Hag Queen \textbar{}
  \protect\hyperlink{Withchbrew}{Witchbrew}}: In your hero phase, you
  can pick a friendly DAUGHTERS OF KHAINE unit within 3" of this model
  to drink.
\end{itemize}

\hypertarget{bewegungsphase}{%
\paragraph{2. Bewegungsphase}\label{bewegungsphase}}

\hypertarget{fernkampfphase}{%
\paragraph{3. Fernkampfphase}\label{fernkampfphase}}

\begin{itemize}
\tightlist
\item
  ACHTUNG, SIR!
\item
  \textbf{The Iron Heart of Khaine: Morathi}, High Oracle of Khaine
  cannot be healed, but no more than 3 wounds can be allocated to her in
  any one turn. Any additional wounds and/or mortal wounds allocated to
  her in the same turn are negated and have no effect.
\item
  \textbf{Gaze of Morathi}: If a target is hit by the Gaze of Morathi,
  pick a model in the target unit and roll a dice. If the result exceeds
  that model's Wounds characteristic, it is slain. \#\#\#\# 4.
  Angriffsphase \#\#\#\# 5. Nahkampfphase \#\#\#\# 6. Kampfschockphase
\end{itemize}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{alligence-abilities}{%
\subsection{Alligence Abilities}\label{alligence-abilities}}

\hypertarget{battle-traits}{%
\paragraph{Battle Traits}\label{battle-traits}}

\begin{itemize}
\item
  \textbf{Fanatical Faith}: Roll a dice each time a wound or mortal
  wound is allocated to a friendly DAUGHTERS OF KHAINE model. On a 6+
  the wound is negated.
\item
  \textbf{Blood Rites}: Cummulative effects for each round

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \tightlist
  \item
    \textbf{Quickening Bloodlust:} Re-roll run rolls of 1 for this unit.
  \item
    \textbf{Headlong Fury:} Re-roll dice rolls of 1 when making charge
    rolls for this unit.
  \item
    \textbf{Zealot's Rage:} Re-roll hit rolls of 1 for this unit. In
    addition, if this unit is an AVATAR OF KHAINE, it always counts as
    being Animated
  \item
    \textbf{Slaughterer's Strength:} Re-roll wound rolls of 1 for this
    unit.
  \item
    \textbf{Unquenchable Fervour:} Re-roll save rolls of 1 for this
    unit. In addition, you do not need to take battleshock tests for
    this unit.
  \end{enumerate}
\end{itemize}

\hypertarget{command-traits}{%
\paragraph{Command Traits}\label{command-traits}}

If the general of a DAUGHTERS OF KHAINE army is a HERO, they can have
one of the following command traits. in addition to any others they
have: - {[} {]} \textbf{Bathed in Blood:} Increase this general's Wounds
characteristic by 1. In addition, at the start of each of your hero
phases, you can heal 1 wound that has been allocated to this general.

\begin{itemize}
\item
  {[} {]} \textbf{Zealous Orator:} Friendly DAUGHTERS OF KHAINE units
  within 14" of this general use this general's Bravery characteristic
  instead of their own.
\item
  {[} {]} \textbf{Bloody Sacrificer:} Add 1 to hit rolls for this
  general's weapons.
\item
  {[} {]} \textbf{Terrifying Beauty:} Subtract 1 from the hit rolls of
  attacks that target this general.
\item
  {[} {]} \textbf{Mistress of Poisons:} Add 1 to the Damage
  characteristics of melee weapons wielded by this general.
\item
  {[} {]} \textbf{True Believer:} This general counts the current battle
  round number as being 1 higher than it actually is when determining
  what abilities they receive from the Blood Rites battle trait (pg 50).
  This is cumulative with other, similar abilities.
\end{itemize}

\hypertarget{lore-of-shadows}{%
\paragraph{Lore of Shadows}\label{lore-of-shadows}}

Each WIZARD in a DAUGHTERS OF KHAINE army knows one spell from the Lore
of Shadows in addition to any others they know. - {[} {]} \textbf{Steed
of Shadows:} Steed of Shadows has a casting value of 5. If successfully
cast, then until the start of your next hero phase, the caster can fly
and has a Move characteristic of 16".

\begin{itemize}
\item
  {[} {]} \textbf{Pit of Shades:} Pit of Shades has a casting value of
  7. If successfully cast, pick an enemy unit within 18" of the caster
  that is visible to them. Roll two dice and add the scores together.
  The enemy unit suffers 1 mortal wound for each point by which the
  total exceeds their Move characteristic.
\item
  {[} {]} \textbf{Mirror Dance:} Mirror Dance has a casting value of 4.
  If successfully cast, pick two friendly DAUGHTERS OF KHAINE HEROES
  within 24" of the caster. So long as neither HERO is within 6" of any
  other unit, the two models can swap positions on the battlefield
  (neither can be set up within 3" of any enemy units).
\item
  {[} {]} \textbf{The Withering:} The Withering has a casting value of
  7. If successfully cast, pick an enemy unit within 18" of the caster
  that is visible to them. Until the start of your next hero phase, add
  1 to wound rolls for attacks that target that unit.
\item
  {[} {]} \textbf{Mindrazor:} Mindrazor has a casting value of 7. If
  successfully cast, pick a friendly DAUGHTERS OF KHAINE unit within 18"
  of the caster. Until the start of your next hero phase, the Rend
  characteristic of that unit's melee weapons is improved by 1. In
  addition, the Damage characteristic of the unit's melee weapons is
  increased by 1 while attacking a target that has a lower Bravery
  characteristic than they do.
\item
  {[} {]} \textbf{Shroud of Despair:} Shroud of Despair has a casting
  value of 4. If successfully cast, pick an enemy unit within 18" of the
  caster that is visible to them. Until the start of your next hero
  phase, subtract 1 from the Bravery characteristic of that unit. If the
  spell was successfully cast with a casting roll of 8 or more, subtract
  D3 from that unit's Bravery instead.
\end{itemize}

\hypertarget{prayers-of-the-khainite-cult}{%
\paragraph{Prayers of the Khainite
Cult}\label{prayers-of-the-khainite-cult}}

Each PRIEST in a DAUGHTERS OF KHAINE army knows one prayer from the six
Prayers of the Khainite Cult in addition to any others they know. A
model that knows such a prayer can pray twice in your hero phase instead
of only once (but not the same spell) - {[} {]} \textbf{Catechism of
Murder} Pick a friendly DAUGHTERS OF KHAINE unit within 14" of the
priest. Until the start of your next hero phase, each time you make a
hit roll of 6 (after re-rolls, but before modifiers are applied) for
that unit in the combat phase, that attack inflicts 2 hits instead of 1.

\begin{itemize}
\item
  {[} {]} \textbf{Blessing of Khaine:} Pick a friendly DAUGHTERS OF
  KHAINE unit within 14" of the priest. Until the start of your next
  hero phase, re-roll failed Fanatical Faith rolls (pg 50) for that
  unit.
\item
  {[} {]} \textbf{Martyr's Sacrifice:} Pick a friendly DAUGHTERS OF
  KHAINE unit within 14" of the priest. Until the start of your next
  hero phase, each time a model from that unit is slain in the combat
  phase, roll a dice. On a 5 or 6 the attacking unit suffers 1 mortal
  wound after it has finished making all of its attacks.
\item
  {[} {]} \textbf{Crimson Rejuvenation:} Pick a friendly DAUGHTERS OF
  KHAINE unit within 14" of the priest (Except Morathi). You can heal up
  to D3 wounds that have been allocated to a model from that unit.
\item
  {[} {]} \textbf{Covenant of the Iron Heart:} Pick a friendly DAUGHTERS
  OF KHAINE unit within 14" of the priest. Until the start of your next
  hero phase, you do not need to take battleshock tests for that unit.
\item
  {[} {]} \textbf{Sacrament of Blood:} Pick a friendly DAUGHTERS OF
  KHAINE unit within 14" of the priest. Until the start of your next
  hero phase, that unit counts the current battle round number as being
  1 higher than it actually is when determining what abilities it
  receives from the Blood Rites battle trait (pg 50). This is cumulative
  with other, similar abilities.
\end{itemize}

\hypertarget{artefacts-of-power}{%
\paragraph{Artefacts of Power}\label{artefacts-of-power}}

If a DAUGHTERS OF KHAINE army includes any HEROES, then one may bear an
artefact of power. \emph{skipping}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{temple}{%
\subsubsection{Temple}\label{temple}}

\begin{itemize}
\tightlist
\item
  {[} {]} \textbf{HAGG NAR}:

  \begin{itemize}
  \tightlist
  \item
    {[} {]} \textbf{Daughters of the First Temple:} Whilst a Hagg Nar
    unit is benefitting from the Zealot's Rage ability from the Blood
    Rites battle trait (pg 50), you can re-roll all failed hit rolls for
    the unit instead of only re-rolling hit rolls of 1.
  \item
    {[} {]} Must have \emph{Devoted Disciples} as command trait:
    Whenever you make a Fanatical Faith roll (pg 50) for a friendly Hagg
    Nar unit within 7" of this general, the wound is negated on a 5+
    instead of a 6+.
  \item
    {[} {]} A Hagg Nar Cauldron Guard battalion (pg 71) can also include
    1 Avatar of Khaine (pg 79) or an additional CAULDRON OF BLOOD.
  \end{itemize}
\item
  {[} {]} \textbf{DRAICHI GANETH:}

  \begin{itemize}
  \tightlist
  \item
    {[} {]} \textbf{Bladed Killers:} Add 1 to hit rolls for Draichi
    Ganeth units in the combat phase if they charged in the same turn.
  \item
    {[} {]} A Draichi Ganeth Slaughter Troupe battalion (pg 72) can also
    include up to 2 units of Witch Aelves.
  \item
    {[} {]} f your army includes any Draichi Ganeth SLAUGHTER QUEENS,
    one must have the artifact \textbf{The Darksword}. This SLAUGHTER
    QUEEN'S Deathsword has an Attacks characteristic of 4.
  \end{itemize}
\item
  {[} {]} \textbf{THE KRAITH:}

  \begin{itemize}
  \tightlist
  \item
    {[} {]} \textbf{Disciples of Slaughter:} Roll a dice after a Kraith
    unit has fought in the combat phase if there are any enemy units
    within 3" of it. On a 6, you can pile in and attack with that unit
    for a second time.
  \item
    {[} {]} A Kraith Cauldron Guard battalion (pg 71) can include any
    number of additional Hag Queens (pg 78). It can also include any
    number of Slaughter Queens (pg 78).
  \item
    {[} {]} One Kraith HERO must have the artifact \textbf{Venom of
    Nagendra}. Once per battle, just before this HERO is chosen to fight
    in the combat phase, she can use the Venom of Nagendra. When she
    does so, choose one of her melee weapons (but not a weapon used by a
    mount). That weapon's Attacks characteristic is 1 for the remainder
    of the phase, but if it hits, the target suffers D6 mortal wounds
    instead of the normal damage.
  \end{itemize}
\item
  {[} {]} \textbf{KHAILEBRON:}

  \begin{itemize}
  \tightlist
  \item
    {[} {]} \textbf{Concealment and Stealth:} Subtract 1 from hit rolls
    that target Khailebron units in the shooting phase.
  \item
    {[} {]} A Khailebron Temple Nest battalion (pg 73) can include up to
    2 additional MELUSAI units.
  \item
    {[} {]} A Khailebron general must have the command trait
    \textbf{Mistress of Illusion:} At the start of your hero phase, you
    can pick a friendly Khailebron unit within 7" of this general. If
    that unit is more than 3" from any enemy models, remove it from the
    battlefield and then set it up anywhere on the battlefield more than
    9" from any enemy models. The unit cannot move in your next movement
    phase. --- \#\#\# Warscroll \#\#\#\#\# WAR COVEN OF MORATHI:
  \end{itemize}
\item
  \textbf{Blood Rituals:} If your army has the DAUGHTERS OF KHAINE
  allegiance, units in this battalion count the current battle round
  number as being 1 higher than it actually is when determining what
  abilities they receive from the Blood Rites battle trait (pg 50). This
  is cumulative with other, similar abilities (e.g.~the True Believer
  Command Trait or the Sacrament of Blood prayer).
\item
  \textbf{Devout Followers:} Do not take a battleshock test for War
  Coven of Morathi units that are within 18" of Morathi (in either of
  her forms) when the test is taken. \#\#\#\#\# CAULDRON GUARD:
\item
  \textbf{Frenzied Devotees:} Add 1 to run and charge rolls made for
  units from this battalion. \#\#\#\#\# SLAUGHTER TROUPE:
\item
  \textbf{Gladiatorial Acrobatics:} Slaughter Troupe units that retreat
  can still shoot and charge in the same turn. \#\#\#\#\# TEMPLE NEST:
\item
  \textbf{Lethal Transfixion:} Each time your opponent makes a hit roll
  of 1 when attacking a Temple Nest unit in the combat phase, the
  attacking unit suffers 1 mortal wound after all of its attacks have
  been made. \#\#\#\#\# SHADOW PATROL:
\item
  \textbf{Shadowpaths:} Once per battle round, instead of moving in your
  movement phase, one unit from this battalion that is more than 3" from
  any enemy models can move along the shadowpaths. If it does so, remove
  the unit from the battlefield, then set it up anywhere on the
  battlefield more than 9" from any enemy models. This is its move for
  that movement phase.
\end{itemize}

\hypertarget{shadowhammer-compact}{%
\subparagraph{SHADOWHAMMER COMPACT:}\label{shadowhammer-compact}}

\begin{itemize}
\tightlist
\item
  \textbf{Righteous Fervour:} In your hero phase, choose one DAUGHTERS
  OF KHAINE unit from this battalion and one STORMCAST ETERNAL unit from
  this battalion that are within 6" of each other. Both units can either
  make a normal move as if it were your movement phase, shoot as if it
  were your shooting phase, or pile in and attack as if it were the
  combat phase. Both units must perform the same action.
\end{itemize}

\hypertarget{library}{%
\section{Library}\label{library}}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{morathi-high-oracle-of-khaine}{%
\subsection{MORATHI, HIGH ORACLE OF
KHAINE}\label{morathi-high-oracle-of-khaine}}

\hypertarget{monstrous-transformation}{%
\subparagraph{Monstrous
Transformation:}\label{monstrous-transformation}}

At the start of your hero phase, Morathi can transform into her
monstrous aspect. See the Morathi, the Shadow Queen warscroll (pg 77)
for a description of how Morathi transforms.

\hypertarget{the-truth-revealed}{%
\subparagraph{The Truth Revealed:}\label{the-truth-revealed}}

If Morathi is wounded, there is a chance she will no longer be able to
contain her wrath and will transform into her monstrous aspect. Roll a
dice at the start of your hero phase. If the result is equal to or less
than the number of wounds currently allocated to Morathi, she transforms
as described on the Morathi, the Shadow Queen warscroll (pg 77).

\hypertarget{the-iron-heart-of-khaine}{%
\subparagraph{The Iron Heart of
Khaine:}\label{the-iron-heart-of-khaine}}

Morathi, High Oracle of Khaine cannot be healed, but no more than 3
wounds can be allocated to her in any one turn. Any additional wounds
and/or mortal wounds allocated to her in the same turn are negated and
have no effect.

\hypertarget{sorceress-supreme}{%
\subparagraph{Sorceress Supreme:}\label{sorceress-supreme}}

Add 1 to casting and unbinding rolls made for Morathi, High Oracle of
Khaine. In addition, double the range of spells she attempts to cast.

\hypertarget{enchanting-beauty}{%
\subparagraph{Enchanting Beauty:}\label{enchanting-beauty}}

Subtract 1 from the hit rolls of attacks that target Morathi, High
Oracle of Khaine.

\hypertarget{arnzipals-black-horror}{%
\subparagraph{ARNZIPAL'S BLACK HORROR}\label{arnzipals-black-horror}}

Arnzipal's Black Horror has a casting value of 7. If successfully cast,
pick an enemy unit within 18" of the caster that is visible to them and
roll a dice. On a1thatunitsuffers1mortalwound,ona2or3it suffers D3
mortal wounds, and on a 4+ it suffers D6 mortal wounds.

\hypertarget{worship-through-bloodshed}{%
\subparagraph{Worship Through
Bloodshed:}\label{worship-through-bloodshed}}

Command Ability. If Morathi, High Oracle of Khaine is your general, you
can use this ability. If you do, pick up to 2 friendly DAUGHTERS OF
KHAINE units within 14" of Morathi. Those units can immediately shoot as
if it were the shooting phase. Alternatively, if either unit is within
3" of an enemy unit, it can instead be chosen to pile in and attack as
if it were the combat phase.

\hypertarget{wizzard}{%
\subparagraph{Wizzard}\label{wizzard}}

Morathi can attempt to cast three spells in your hero phase, and attempt
to unbind two spells in the enemy hero phase. She knows the Arcane Bolt,
Mystic Shield and Arnzipal's Black Horror spells.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{morathi-the-shadow-queen}{%
\subsection{MORATHI, THE SHADOW QUEEN}\label{morathi-the-shadow-queen}}

\hypertarget{monstrous-revelation}{%
\subparagraph{Monstrous Revelation:}\label{monstrous-revelation}}

\hypertarget{gaze-of-morathi}{%
\subparagraph{Gaze of Morathi:}\label{gaze-of-morathi}}

If a target is hit by the Gaze of Morathi, pick a model in the target
unit and roll a dice. If the result exceeds that model's Wounds
characteristic, it is slain.

\hypertarget{the-iron-heart-of-khaine-1}{%
\subparagraph{The Iron Heart of
Khaine:}\label{the-iron-heart-of-khaine-1}}

Morathi, the Shadow Queen cannot be healed, but no more than 3 wounds
can be allocated to her in any one turn. Any additional wounds and/or
mortal wounds allocated to her in the same turn are negated and have no
effect.

\hypertarget{wizzard-1}{%
\subparagraph{Wizzard}\label{wizzard-1}}

Morathi the shadow queen can attempt to cast one spell in your hero
phase, and attempt to unbind one spell in the enemy hero phase. She
knows the Arcane Bolt, Mystic Shield and Arnzipal's Black Horror spells.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{hag-queen}{%
\subsection{HAG QUEEN}\label{hag-queen}}

\hypertarget{priestess-of-khaine}{%
\subparagraph{Priestess of Khaine:}\label{priestess-of-khaine}}

In your \protect\hyperlink{1.-Heldenphase}{hero phase}, a Hag Queen can
pray once. If she does, pick a prayer she knows and roll a dice. On a
result of 1 she is found unworthy and suffers 1 mortal wound. On a 2
nothing happens. On a 3+ the prayer is successful and its effect takes
place. A Hag Queen knows the Rune of Khaine and Touch of Death prayers:
\protect\hyperlink{Rune-of-Khaine:}{Rune of Khaine} and
\protect\hyperlink{Touch-of-Death:}{Touch of Death}

\hypertarget{rune-of-khaine}{%
\subparagraph{Rune of Khaine:}\label{rune-of-khaine}}

The Hag Queen's Blade of Khaine has a Damage characteristic of D3
instead of 1 until your next hero phase.

\hypertarget{touch-of-death}{%
\subparagraph{Touch of Death:}\label{touch-of-death}}

Pick a unit within 3" of this model and then hide a dice in one of your
hands. Your opponent must pick a hand; if that hand is holding the dice,
the unit you picked suffers D3 mortal wounds.

\hypertarget{witchbrew}{%
\subparagraph{Witchbrew:}\label{witchbrew}}

In your \protect\hyperlink{1.-Heldenphase}{hero phase}, you can pick a
friendly DAUGHTERS OF KHAINE unit within 3" of this model to drink
witchbrew. If you do, then until your next hero phase you can re-roll
failed wound rolls for that unit's melee weapons, and you do not need to
take battleshock tests for the unit.

\hypertarget{slaughter-queen}{%
\subsection{SLAUGHTER QUEEN}\label{slaughter-queen}}

\hypertarget{avatar-of-khaine}{%
\subsection{AVATAR OF KHAINE}\label{avatar-of-khaine}}

\hypertarget{hag-queen-on-cauldron-of-blood}{%
\subsection{HAG QUEEN ON CAULDRON OF
BLOOD}\label{hag-queen-on-cauldron-of-blood}}

\hypertarget{witch-aelves}{%
\subsection{WITCH AELVES}\label{witch-aelves}}

\hypertarget{sisters-of-slaughter}{%
\subsection{SISTERS OF SLAUGHTER}\label{sisters-of-slaughter}}

\hypertarget{slaughter-queen-on-cauldron-of-blood}{%
\subsection{SLAUGHTER QUEEN ON CAULDRON OF
BLOOD}\label{slaughter-queen-on-cauldron-of-blood}}

\hypertarget{bloodwrack-shrine}{%
\subsection{BLOODWRACK SHRINE}\label{bloodwrack-shrine}}

\hypertarget{blood-sisters}{%
\subsection{BLOOD SISTERS}\label{blood-sisters}}

\hypertarget{blood-stalkers}{%
\subsection{BLOOD STALKERS}\label{blood-stalkers}}

\hypertarget{bloodwrack-medusa}{%
\subsection{BLOODWRACK MEDUSA}\label{bloodwrack-medusa}}

\hypertarget{doomfire-warlocks}{%
\subsection{DOOMFIRE WARLOCKS}\label{doomfire-warlocks}}

\hypertarget{khinerai-heartrenders}{%
\subsection{KHINERAI HEARTRENDERS}\label{khinerai-heartrenders}}

\hypertarget{khinerai-lifetakers}{%
\subsection{KHINERAI LIFETAKERS}\label{khinerai-lifetakers}}
